\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[T1]{fontenc}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Andres Cruz} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ +1-786-262-0053 ~ 
    \href{mailto:acruz24100@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{acruz24100@gmail.com}} ~ 
    \href{https://andrescruz.xyz/}{\raisebox{-0.2\height}\faGlobe\ \underline{andrescruz.xyz}} ~ 
    \href{https://github.com/cruz-andr}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/cruz-andr}} \\
    \vspace{2pt}
    \small Boston, MA $\mid$ \textbf{Available for Internship: May -- December 2026}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University}{Boston, MA}
      {B.S. Computer Science w/ concentration in AI and minor in Math}{Sep 2024 -- May 2028}
      \resumeItemListStart
        \resumeItem{\textbf{GPA: 3.84/4.0}}
        \resumeItem{\textbf{Relevant Coursework:} Algorithms \& Data Structures, Differential Equations, Linear Algebra, Physics for Engineering, Embedded Systems, Artificial Intelligence, Object-Oriented Design (C++/Java).}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS----------- 
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} C/C++ (Strong), Python, CUDA, MATLAB, SQL, JavaScript \\
     \textbf{Robotics \& Simulation:} ROS2, Gazebo, OpenCV, IMU Sensor Fusion, PID Control, Kinematics \\
     \textbf{Hardware \& Embedded:} Raspberry Pi, ESP32, Arduino, I2C/SPI/UART, SolidWorks, Fusion 360 \\
     \textbf{Tools \& Platforms:} Linux (Ubuntu), Git, Docker, AWS IoT Core, PyTorch
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Engineering Projects}
    \resumeSubHeadingListStart

      \resumeProjectHeading
          {\textbf{AI Academic Constraint Solver} $|$ \emph{React.js, Node.js, LLM Agents}}{2025 -- Present}
          \resumeItemListStart
            \resumeItem{Building a logic-constrained AI agent to parse complex requirements and generate optimized schedules.}
            \resumeItem{Applying prompt engineering and logical constraints to ensure zero-hallucination outputs for critical planning.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Prime Intellect (Open Source AI)} $|$ \emph{Python, PyTorch, LLMs}}{2025}
          \resumeItemListStart
            \resumeItem{Contributed to the \textbf{Prime Intellect} repository, focusing on evaluation modes for Large Language Model benchmarking.}
            \resumeItem{Optimized Python scripts to improve reproducibility of research metrics for the open-source AI community.}
            \resumeItem{Gained deep familiarity with model evaluation pipelines, relevant for Validating Sim-to-Real gaps.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Custom Bipedal Robot Prototype} $|$ \emph{C++, Python, SolidWorks, IMU}}{2023 -- Present}
          \resumeItemListStart
            \resumeItem{Designed and fabricated a bipedal robotic platform using custom 3D-printed mechanical linkages and servo actuators.}
            \resumeItem{Developed stabilization algorithms in \textbf{C++} using IMU feedback loops to maintain balance and correct posture.}
            \resumeItem{Engineered the power distribution system and integrated a Raspberry Pi for high-level logic and gait planning.}
            \resumeItem{Modeled all components in \textbf{SolidWorks} to ensure mechanical feasibility and center-of-mass optimization.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Computer Vision Security System} $|$ \emph{OpenCV, Python, IoT}}{2022 -- 2024}
          \resumeItemListStart
            \resumeItem{Engineered a facial recognition entry system using \textbf{OpenCV} to automate access control with low latency.}
            \resumeItem{Integrated sensor data streams via \textbf{MQTT} to a central hub for real-time monitoring of environmental states.}
            \resumeItem{Reduced false-positive detections by optimizing image pre-processing pipelines before model inference.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Warehouse Automation Lead (Safety Supervisor)}{Jul 2020 -- May 2024}
      {All Florida Paper}{Medley, FL}
      \resumeItemListStart
        \resumeItem{Designed and deployed an automated monitoring system using sensors and cameras to track workflow efficiency.}
        \resumeItem{Utilized Python scripts to automate inventory tracking, reducing manual data entry errors by 25\%.}
      \resumeItemListEnd
  
    \resumeSubheading
      {Full-Stack Development Intern}{Jun 2023 -- Aug 2023}
      {Florida International University}{Miami, FL}
      \resumeItemListStart
        \resumeItem{Architected data visualization dashboards for IoT device monitoring, processing real-time sensor streams.}
        \resumeItem{Optimized backend API performance in Node.js, reducing latency for critical data retrieval by 40\%.}
        \resumeItem{Documented system architecture and API endpoints to facilitate handoff to engineering teams.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------INTERESTS-----------
\section{Interests}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{Humanoid Robotics • Physics Simulation • Open Source AI • Embedded Systems • Rapid Prototyping}}
 \end{itemize}

\end{document}